Computer Science House By-Laws

### 2013-05-24 bylaws.tex
Fixed date, and allowed for cross-document hyperlinking

\documentclass{article}
% The xr package allows external references
\usepackage{xr}

@@

% Define the external document to be constitution for cross referencing purposes
\externaldocument{constitution}

% Title page information
\title{Computer Science House By-Laws}
\author{Computer Science House Executive Board}
% Last Modified Date
\newcommand{\datechanged}{Monday, April 5, 2004}
\date{\datechanged}

@@

% Headings
\pagestyle{myheadings}
\markright{{\rm CSH Constitution \hfill  As of \datechanged \hfill Page }}
% Reference example:
%Test reference \ref{House Objectives} House Objectives.

@@

% By-Laws
\bylaw{By-Law Structure}
By-Laws define the more flexible aspects of the House. Any semantic change to a by-law requires the change to be proposed at a House Meeting, discussed, followed by a House vote as described in \ref{Voting}, Voting. A by-law may be overridden by an immediate House vote with a quorum of sixty-six percent of the number of all House members privileged to vote. A vote equaling or exceeding sixty-six percent of all House members present during the vote is required for the override to go through. The By-Laws are arranged by section with each section of By-Laws pertain to a particular governing aspect of the House

\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the ten weeks of Fall, Winter, and Spring Academic Quarters.  The Summer Academic Quarter, all between Quarter Interim, and all end of Quarter Exam Weeks are considered Non-Standard Operating Session.  Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.

\bylaw{Operations of the Executive Board}
\bsection{Weekly Notes}
The Executive Board members are expected to submit to the House, notes for their meetings each week.
\bsection{The House Rules}
The House Rules shall contain the following information:
\begin{itemize}
\item The Section of \ref{Membership} Membership that corresponds to the membership status of the signing member.
\item The explanatory paragraph from \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process} describing the Evaluation Process
\item The Computer Science House Code of Conduct Sheets pertaining to responsible utilization of the Computer Science House and Rochester Institute of Technology facilities.
\end{itemize}
\bsection{Closed Executive Board}
\newcommand{\writeoutref}{\ref{Executive Board}, \ref{Voting Members},}
\bsubsection{Closed Executive Board Meetings are open only two the Chairman and Voting Members of the Executive Board as deﬁned in Article 6, Section A, Subsection 3, and those with express permission of the Executive Board. }

\bsubsection{A closed Executive Board meeting may be called at any time by any member of the Executive Board.  However, the Chairman and at least two-thirds of the Voting Members as defined in Article 6, Section A, Subsection 3 must be present for a meeting to be called.}

\bylaw{Operations of the Financial Committee}
\bsection{Amount of House Dues}
The amount of dues for Resident Members is thirty dollars (\$35.00) per Academic Quarter.  The amount of dues for Non-Resident Members is twenty-five dollars (\$30.00) per Academic Quarter.
\bsection{Collection of House Dues}
The Financial Director is responsible for ensuring the House is notified of the due date for the payment of House dues at least two weeks in advance of the actual due date. If a member is unable to pay House dues by the due date, he or she should contact the Financial Director prior to the due date or his or her payment will be considered delinquent.
\\* \\*
If the Financial Director determines that the member's reason for inability to pay House dues is sufficient, an extended due date will be set for that member. If the Financial Director determines the reason to be insufficient, the member may appeal the Executive Board. If the Executive Board upholds the Financial Director's ruling, then the member's payment is considered delinquent. If the Executive Board overrides the Financial Director's ruling, the Executive Board will set an extended due date for that member.
\\* \\*
If the member again finds himself or herself unable to pay dues at the time of the extended due date, he or she may follow the same procedure for the first extension.
\\* \\*
If a member's payment goes delinquent for any of the above reasons, his or her case is brought before the Executive Board, and action may be taken at the discretion of the Executive Board. The Financial Director should be present at this hearing. If the initial House judicial board feels it is unable to adequately resolve the case, or the member wishes to appeal any ruling by the initial House judicial board, the case may be presented to the Executive Board as the final House judicial board.
\\* \\*
The Executive Board has the authority to enforce House sanctions up to and including revocation of House privileges and/or the removal of membership status. Once the dues have been paid, the judicial board has the option of dropping all current sanctions or continuing the current sanctions until they have been completed. The Executive Board may not continue to render new sanctions once the dues have been paid.
\bsection{Breakdown of Dues for Committee Budgets}
\begin{center}
\begin{tabular}[c]{l c}
Committee or Budget Name & Percentage of Dues \\
\hline
\hline
Operational Communications &	19\% \\
\hline
Evaluations \& Selections & 4\% \\
\hline
House History & 9\% \\
\hline
House Improvements & 9\% \\
\hline
Research and Development & 19\% \\
\hline
Miscellaneous & 5\% \\
\hline
House Accum. & 10\% \\
\hline
Social & 25\% \\
\hline
\end{tabular}
\end{center}
\bsection{Expenditure Approval}
All House expenditures must be approved by the financial director and the director responsible for the budget from which the funds will be drawn. If any single expenditure exceeds fifty dollars (\$50.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated. If any total expenditure exceeds seventy-five dollars (\$75.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated. A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
\\* \\*
Any project requiring more than \$300 in total funding from CSH must include a Complete Project proposal, including a Project Budget, Timeline and Resources needed. The person requesting the funds must then report to executive board once per week on the progress of the project.

\bylaw{Operations of the Evaluations Committee}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for an applicant or new member to meet existing House members, learn House history, demonstrate their involvement potential in the House, and allow existing House members to meet and evaluate the applicant or new member.

@@

The Evaluations Committee chooses between 1 and 3 House members to be Introductory Process Advisors. The advisors organize the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.  All participants will receive an Intro. Packet minimally containing the following information:
\begin{itemize}
\item A description of the History of Computer Science House
\item A list of all Resident members, as defined in Article V, Membership.
\item The Computer Science House Constitution and By-Laws.
\item The Computer Science House Dictionary
\end{itemize}
The Introductory Process lasts for a minimum of six weeks from the initiation of the process, until the participant has completed all of the following requirements. The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process based on requirements listed in the Introductory Process Proposal. However, the Introductory Project must be complete before the Introductory Evaluation occurs.

@@

The participant is given 2 weeks complete the following lists, termed the Intro. Sheets:
\begin{itemize}
\item For each Resident member, Executive Board member, and for Fifteen Non-Resident and Alumni members (in addition to Non-Resident Executive Board Members), list:
\begin{itemize}
\item The member's home town
\item The members local room and phone, or address as applicable
\item The member's major and year
\item The House committee(s) the member is interested in
\item A question of your own to get to know the member
\item The member's signature.
\end{itemize}
\item For each House committee, list:
\begin{itemize}
\item The full name of the committee
\item Some of the responsibilities of the committee
\item The name of the committee's director
\item The weekly meeting time and place
\end{itemize}
\item Seven annual Computer Science House social events
\item Seven major Computer Science House technical achievements
\end{itemize}
The participant is also expected to be involved in the following:
\begin{itemize}
\item  Attend all House meetings during the process
\item  Attend at least one House committee meeting each week of the process
\item  Attend at least one House social event during the process
\item  Show an acceptable amount of participation in at least one Technical Project.  Acceptable participation is determined by the project leader and the Introductory Evaluation Process described in By-Law V, Section F, Subsection 5.  This project is in addition to the Technical Project required for all Resident and Non-Resident members as stated in By-Law V, Section G.
\end{itemize}
The participant is also expected to be involved in the Introductory Project. The Introductory Project is an annual fundraiser that takes place during the Fall Quarter Introductory Process. It is organized and carried out by all Introductory Process participants. All of the proceeds go to a charity chosen in advance by the participants. The participants must elect a non-voting Executive Board Representative, termed the Freshman President who is required to represent the Introductory Process participants on the Executive Board. The Freshman President is responsible for any internal Introductory Project duties as well as for bringing a written Introductory Project Proposal to the Executive Board. The Executive board will hold discussion followed by a closed ballot Simple Majority Vote according to \ref{Voting} Voting, \ref{Simple Majority Vote} Simple Majority Vote, to determine if the proposed project fulfills the Introductory Project requirements.

@@

At the end of the Introductory Period, there will be an Introductory Evaluation, described in By-Law V, Section F, Subsection 5, to determine which members will be extended offers of full membership.

\bsection{Selection Process for Students Attending RIT for at Least One Quarter}
\bsubsection{The applicant submits an application to the Evaluations Committee for review.}
\bsubsection{The applicant participates in an informal interview with exactly three current Resident, Non-Resident, Alumni, or Honorary Members.}
\bsubsection{The Evaluations Committee then meets and reviews all of the application materials and decides whether to accept the person as a special introductory member.}
\bsubsection{The applicant is interviewed again, no less than 10 weeks after acceptance to the introductory process, by three different persons meeting the same requirements as for the first interview. The purpose of this interview is to determine if the applicant has shown sufficient interest and work to merit becoming a full Resident or Non-Resident Member.}
\bsubsection{The Evaluations Committee reviews all information regarding the applicant and if the applicant is found to be a positive influence on House objectives or morale; accepts the applicant to either full Resident or Non-Resident membership, rejects the applicant, or extends the introductory process for the applicant until the next fall quarter, during which time the applicant must participate in the introductory process used by introductory members during fall quarter.}
Note: Most membership privileges do not initiate until successful completion of the introductory process. This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum. The member does, however, have the right to use Computer Science House's facilities. The member must also pay dues. 
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

\bsection{Selection Process for First Quarter and Entering RIT Students}
\bsubsection{The applicant submits an application to the Evaluations Committee for review. The preferred application time is during the previous academic year up to one week prior to the Department of Residence Life's Deadline for Acceptance of Entering Students into Special Interest Houses.}
\bsubsection{The applicant participates in an informal interview with exactly three current Resident, Non-Resident, or Alumni members.}
\bsubsection{The application and interview is reviewed by the Evaluations Committee to make a decision on either the granting or denial of membership in the House. The applicant is notified of the committee's decision within three weeks after the Department of Residence Life's Deadline for Acceptance of Entering Students into Special Interest Houses.}
\bsubsection{The applicant moves onto the House Fall Quarter and is granted full membership privileges and responsibilities including House dues, combinations, and accounts. In addition to these privileges and responsibilities, the new member must participate in the Introductory Process.}
\bsubsection{During the Introductory Evaluation Process, the new member's Introductory Process will be used to aid in evaluating their membership. If the new member has unsuccessfully completed the Introductory Process or has been found to be a detriment to House objectives or morale, the person's membership may be revoked pursuant to the Membership Revocation Process and the person would be asked to find alternative housing as soon as possible in accordance with all applicable Residence Life Policies regarding room changes. If the new member has completed the Introductory Process, passes the Introductory Evaluation Process and is not found to be a detriment to House objectives or morale, it is announced at the following House meeting and appropriate traditions are upheld.}
Note: Most membership privileges do not initiate until successful completion of the introductory process. This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum. The member does, however, have the right to use Computer Science House's facilities. The member must also pay dues. 
\\* \\*
Additional Note: Any member who has not been subject to at least one Objective Evaluation (Spring Evaluations) cannot become an Alumni. Instead, if the member moves off floor, the member becomes a Non-Resident member. This is only true of persons who have not gone through the Objective Evaluation Process at some point during their Computer Science House membership.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

\bsection{Selection Process for Honorary Members}
\bsubsection{A House Member submits to the Evaluations Committee, a nomination for a person they feel is deserving of Honorary Membership.}
\bsubsection{The Evaluations Committee performs some preliminary research on the candidate and presents the finding.}
\bsubsection{The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote. If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.}
\bsubsection{The nomination is presented at a House meeting for discussion. Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period. A quorum of two-thirds the number of all House members eligible to vote is required for the vote to be official. A vote equaling or exceeding two-thirds the number of all ballots cast is required for the candidate to be granted Honorary Membership.}
\bsubsection{The candidate is notified of their selection as an Honorary Member and presented with the honor.}

\bsection{Selection Process for Advisory Members}
\bsubsection{A House Member submits to the Executive Board, a nomination for a person who they feel would benefit the House as an advisor during the period of time provided for by Article V, Section F, Subsection 2 Advisory Membership Selection.}
\bsubsection{After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.}
\bsubsection{A discussion of the candidates will be held at the following House meeting.}
\bsubsection{Ballots will then be distributed for a secret ballot House vote. The vote is a fifty-percent vote meaning a quorum of fifty percent of the number of all House members eligible to vote is required for the selections to be official. A vote for the selection of a specific candidate equaling or exceeding fifty percent of the number of ballots cast is required for the respective advisor candidate to be selected. If more than two advisors are selected via this process, the Executive Board may call for a revote amongst the candidates selected in order to reduce the number of advisors to a workable level. If this decision is made, the candidates selected in the first ballot become the nominees for the second ballot and Step Three and Four are repeated. This recast process may not be repeated a second time.}
\bsubsection{All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection. If one or more selected candidates decline the position, the Executive Board may begin a selection process for additional advisors. Note that selected candidates who accept their selection remain selected, this additional selection process is only a means to bring the number of advisors up to a workable level. If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.}

\bsection{Evaluations Process}
During the academic year, a House member is evaluated by two different processes. The first process, known as the Subjective Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House. The second process, known as the Objective Evaluation, is responsible for determining those individuals who will be offered residence on the House for the next academic year. These processes are separate from each other and should not interfere with one another, with the exception that the Subjective Evaluation is used to provide information for the Objective Evaluation.

@@

At the beginning of any Evaluation Process listed herein, the director of the Evaluation Committee must read the sections of the Computer Science House Constitution and By Laws used during the respective Evaluation Process.
\bsubsection{Subjective Evaluation}
The subjective evaluation process occurs during the academic year. It is performed mid Winter Quarter. The members of the Evaluations Committee, on a member by member basis, review the project logs for projects on which the member was involved, along with the member's activity worksheet and any other information the member chooses to provide. Each active House member will receive two Housing Points (see By-Law V, Section F). The Evaluation Committee may also award one bonus point if it decides that this house member has performed a large or exceptional amount of work for the house. The committee may also deduct one housing point from any House member who has not performed an acceptable amount of work for the house. The guidelines of the committees will be used as a guide in determining bonus and deducted points. No housing points will be awarded to members who do not return the Evaluation Activity Sheets.

@@

Any house member not living on-floor, for example, because a leave of absence for CO-OP, during the quarter of Subjective Evaluations will be evaluated by these criteria and awarded their share of housing points near the end of the quarter in which they return.

@@

A quorum of two-thirds of all Resident and Non-Resident (except for Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.

@@

All votes during the Subjective Evaluation Process must be Closed Ballot, Three Tiered Vote as defined in Article VIII, Section C, Subsection 4. The votes will be counted by the Evaluations Director and two randomly chosen vote counters from the Evaluation Process Participants.
\bsubsection{Objective Evaluation}
The objective evaluation process occurs once per academic year. It is performed as part of the Evaluation Process that takes place during the middle of spring quarter. The Evaluation Committee, on a member by member basis, ensures that each member has met the minimum requirements in order to be placed on the housing list for the following year. These requirements are detailed in Article V under expectations for each category of membership. These requirements must be completed by the seventh week of Spring Quarter when objective evaluations will occur.

@@

A quorum of two-thirds of all Resident and Non-Resident (except for Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.

@@

All votes during the Objective Evaluation Process must be Closed Ballot, Simple Majority Vote as defined in Article VIII, Section C, Subsection 1. The votes will be counted by the Evaluations Director and two randomly chosen vote counters from the Evaluation Process Participants.
\bsubsection{Responsibilities of Members and Directors}
Each member will be required to complete a form known as the activity worksheet for each Subjective Evaluation. This form is a list of what projects the member participated in since the last evaluation period, and should detail the level of involvement in each project. After being verified by the appropriate directors, the Evaluation Committee will include this list in its review of the member.

@@

\textbf{It is incumbent upon each House member to provide the Evaluation Committee with whatever information he or she feels is necessary to ensure an accurate evaluation.}
For every House project there will be created a project log. It minimally contains information describing the project as well as the project leaders and participants, and should detail the participants involvement with the project. The project log is to be submitted to the appropriate director. If an appropriate director does not exist, the project log is to be submitted to the chairman. It is the director's responsibility to ensure that a project log is created and submitted for every House project that falls under that director's jurisdiction.
If a member disagrees with the outcome of any evaluation, (e.g. is not asked to return to the House for the following year) and wishes to appeal the decision, he or she should immediately contact the Evaluations Director, the House Manager, or the Chairman. At the following Executive Board meeting, the member will present his appeal to the Board. The Executive Board can uphold, overturn or conditionally overturn the Evaluation Committee's decision with a secret ballot Two Thirds Vote as described in Article VIII, Section C, Subsection 3. If the decision is overturned or conditionally overturned, the member is to be added to the housing list immediately.

>>>>

\documentclass{article}
% The xr package allows external references
\usepackage{xr-hyper}
\usepackage{hyperref}

@@

% Define the external document to be constitution for cross referencing purposes
\externaldocument{constitution}[https://github.com/ComputerScienceHouse/Constitution/blob/master/constitution.pdf?raw=true]

% Title page information
\title{Computer Science House By-Laws}
\author{Computer Science House Constitution Committee}
% Last Modified Date
\newcommand{\datechanged}{Last Updated \today}
\date{\datechanged}

@@

% Adding a \bsubsubsection -- I feel dirty
\setcounter{secnumdepth}{5}
\newcommand{\bsubsubsection}[1]{\paragraph{#1} \label{#1}}
\renewcommand{\theparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}}

% Headings
\pagestyle{myheadings}
\markright{{\rm CSH Constitution \hfill \datechanged \hfill Page }}
% Reference example:
%Test reference \ref{House Objectives} House Objectives.

@@

% BY-LAW I - INTRODUCTION
\bylaw{Introduction}
By-Laws will expand upon, while not redefining, Articles laid out in the Constitution. By-Laws provide additional depth and definition to the processes and operations of House.

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the fifteen weeks of Fall and Spring semesters. The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions. Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.

% BY-LAW III - OPERATIONS OF THE FINANCIAL DIRECTORSHIP
\bylaw{Operations of the Financial Directorship}
\bsection{Amount of House Dues}
The amount of dues for Active Members living on floor will be fifty-five dollars (\$55.00) per Academic Semester. The amount of dues for Active Members living off floor twill be fifty dollars (\$50.00) per Academic Semester.
\bsection{Collection of House Dues}
At the start of the academic year, dues for on-floor members (for both semesters) are collected through the member’s RIT bill. Dues for off-floor members are to be collected at the start of each semester by the Financial Director. For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
\\*\\*
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director. If the Financial Director deems their situation appropriate, they may grant an extension for payment. If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board. If the Executive board disagrees with the Financial Director, the Executive board may grant an extension. If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made. This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
\bsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{l c}
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Accumulated & 10\% \\
\hline
\end{tabular}
\end{center}

The suggested total operational budget is \$5544. This figure is based on yearly estimated on-floor member dues (\$110 x 56 members = \$6160) minus the 10\% reserved for Accumulated (Accum). Money allocated for Accum and off-floor member dues are deposited into the CSH Account and saved.

\bsection{Expenditure Approval}
All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn). Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100). A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}. It is required that, for expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting. This proposal includes the project budget, inventory of required resources, and a timeline for completion. It is also recommended that all expenditure approvals done at House meeting, regardless of amount, provide such a proposal.
\\* \\*
If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount. Miscellaneous purchases are deducted directly from the CSH Account, and therefore must have final approval of the Financial Director.
\\* \\*
Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\bylaw{Operations of the Evaluations Directorship}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for introductory members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\bsubsection{The Evaluation Period}
The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it. The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
\bsubsection{The Introductory Project}
Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
\bsubsection{Introductory Executive Board}
An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project. The Introductory Executive Board consists of three members:
\begin{itemize}
	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
	\item A Vice President, who assists the President in leadership and representation.
	\item A Treasurer, who manages the finances for the project.
\end{itemize}
Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
\bsubsubsection{The Project} 
The Project is an annual fundraising event that takes place in the first semester of the Introductory Process. All of the proceeds go to a charity chosen in advance by the participants. The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
\bsubsubsection{Introductory Project Advisors} 
The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors. The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
\bsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
\begin{itemize}
	\item A signature from: all Resident members, each Executive Board member, all Introductory members who reside on Floor, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
	\item A description of each Executive board position, including:
	\begin{itemize}
		\item The responsibilities of the position
		\item The name(s) of the position’s member(s)
		\item The position’s weekly meeting time
	\end{itemize}
	\item A list of seven (7) annual House social events
	\item A list of seven (7) major House technical achievements
\end{itemize}
\bsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Be an active participant in an the Introductory Project
\item Attend at least one House directorship meeting for each week of the process
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations.
\end{itemize}
The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership. Occurs once per academic year as part of the Introductory Process.
\bsubsubsection{Voting} 
On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}. A Simple Majority vote with a quorum of two-thirds of all Active members is required for the evaluation to be valid. Neither absentee nor proxy votes are allowed. House may choose any of the Outcomes for each member.
\bsubsubsection{Outcomes} 
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
	\item If an Introductory Member fails to meet the requirements, his membership will be revoked. In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements. A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House. Each conditional consists of a set of additional requirements a deadline for completing them. When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness. A conditional member who does not meet these additional requirements forfeits membership.
\end{enumerate}
\bsection{Selection Processes}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\bsubsection{Selection Process for Students Attending RIT for at Least One Semester}
\begin{enumerate}
	\item The applicant submits an application to the Evaluations Director for review.
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
	\item The application materials are then reviewed at an Evaluations meeting and the members present vote on whether to accept the person as an introductory member.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the introductory process. This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum. The member does, however, have the right to use Computer Science House's facilities. The member must also pay dues.

@@

Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
\bsubsection{Selection Process for First Semester and Entering RIT Students}
\begin{enumerate}
	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee. The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}. An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the introductory process. This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum. The member does, however, have the right to use Computer Science House's facilities. The member must also pay dues.

@@

Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
\bsubsection{Selection Process for Honorary Members}
\begin{enumerate}
	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote. If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}. Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
	\item The candidate is notified of their selection as an Honorary Member and presented with the honor.
\end{enumerate}
\bsubsection{Selection Process for Advisory Members}
\begin{enumerate}
	\item When there is a perceived need, the Executive Board may open nominations for Advisory Members. After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
	\item After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.
	\item A discussion of the candidates will be held at the following House meeting.
	\item Ballots will then be distributed for a secret ballot, fifty-percent House vote, as defined in \ref{Fifty Percent}. If more than two advisors are selected via this process, the Executive Board may call for a revote amongst the candidates selected in order to reduce the number of advisors to a workable level. If this decision is made, the candidates selected in the first ballot become the nominees for the second ballot and Step Three and Four are repeated. This recast process may not be repeated a second time.
	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection. If one or more selected candidates decline the position, the Executive Board may begin a selection process for additional advisors. Note that selected candidates who accept their selection remain selected, this additional selection process is only a means to bring the number of advisors up to a workable level. If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.
\end{enumerate}

\bsection{Evaluations Processes}
During the academic year, a House member is evaluated by two different processes. The first process, known as the Housing Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House. The second process, known as the Membership Evaluation, is responsible for determining those individuals who will have the option to continue Active Membership in the following year. These processes are separate from each other and should not interfere with one another. Semi-Annual Evaluations Meetings are open only to all current Active Members. All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.

@@

At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process. It is incumbent upon each House member to provide the Evaluation Director with whatever information he or she feels is necessary to ensure an accurate evaluation.
\bsubsection{Housing Evaluation}
The Housing Evaluation process occurs during the academic year. It is performed late Fall Semester after the Introductory Evaluation and is led by the Evaluations Director. The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).

@@

All Active members who wish to be evaluated are required to submit an activity report in which they may log projects worked on, social events and seminars hosted or attended, and any other information they deem relevant. A member’s failure to submit the activity report will result in that member receiving no housing points. Attendance is also required for a member to be evaluated, else they will receive no housing points. Any member unable to attend because of outstanding circumstances (e.g. away on co-op) may also submit an activity report and be voted on, though they may not vote. Members in this situation should contact the Evaluations Director at least one day prior to the evaluation.

@@

The participating members, on a member by member basis, review the activity report provided by each member. The participating members may then choose to award one, two, or three housing points to each member. Points are awarded on the basis of contributions to House. Above average members receive three points, average members two points, and below average members one point.

@@

A quorum of two-thirds of all Active (excluding Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.

@@

All votes during the Housing Evaluation Process must be Closed Ballot, Three Tiered Vote as defined in \ref{Three Tiered}.
\bsubsection{Membership Evaluation}
The Membership Evaluation process occurs once per academic year. It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
\bsubsubsection{Voting} 
A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year. All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.These requirements are detailed in Article V under expectations for each category of membership. These requirements must be completed before the Membership Evaluation occurs. A secret Simple Majority vote with a quorum of two-thirds of all Active members is required for the evaluation to be valid. Neither absentee nor proxy votes are allowed. House may choose any of the Outcomes for each member.
\bsubsubsection{Outcomes}
Members who receive a pass have the option participate as an Active Member in the following the year and remain on the upcoming roster if applicable.

@@

If a member fails and has never passed an Membership Evaluation in the past, his membership will be revoked at the end of the year. If the member has previously passed an Membership Evaluation he will move to Alumni Membership status. In either case, the member forfeits his ability to be included on the following year’s roster.

@@

A member may be given a conditional to complete as a means of making up for missing requirements. A conditional may be proposed by any member present at the Evaluation and, if it is approved by the Evaluations Director, is then voted on by House. Each conditional consists of a set of additional requirements a deadline for completing them. When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness. A conditional member who does not meet these additional requirements will have failed the evaluation.
If a member disagrees with the outcome of any evaluation, (e.g. is not asked to return to the House for the following year) and wishes to appeal the decision, he or she should immediately contact the Evaluations Director or the Chairman. At the following Executive Board meeting, the member will present his appeal to the Board. The Executive Board can uphold, overturn or conditionally overturn the Evaluation decision with a Simple Majority Vote as described in \ref{Simple Majority}.

@@

If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the Area Coordinator

\bsection{Expectations of House Members}
Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings. Members are also required to actively participate in a majority of House activities.
\\* \\*
The member must participate significantly in at least one major House project during the academic year. The member is required to submit a description for this major project to the Executive Board for approval. As an option to this requirement, the member may instead assist on a large number of House activities and projects. However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year. This participation will be evaluated by the Executive Board.
